Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-03-18 inst/doc/policycosts/policycosts.Rnw
updates from previous runs

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}

@@

\begin{figure}
<<Figure_7>>=
require(ggplot2)
df <- read.csv("output.csv")
df2 <- df[c("penalty_fn", "ignore_cost", "assume_cost", "sigma_g", "reduction")] # subset
df3 <- reshape2::melt(df2, id = c("penalty_fn", "sigma_g", "reduction")) 
df3$reduction <- as.factor(df3$reduction)
ggplot(df3) + 
  geom_line(aes(sigma_g, value, col=reduction, lty=variable)) +
  #facet_grid(reduction~penalty_fn, scales="free")
  facet_wrap(~penalty_fn, scales="free_y", ncol=1) +
  scale_y_continuous(limits=c(-3e4,3e4))

  @
\end{figure}

@@

<<Table_1, results="asis">>=
df4 <- df[c(1,2,4,6,7)]
df4 <- plyr::arrange(df4, penalty_fn)
print(xtable::xtable(df))
@

>>>>

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}
<<settings, echo=FALSE, warning=FALSE>>=
require(knitr)
opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
require(plyr)
require(xtable)

theme_set(theme_bw())
@

<<maincode, echo=FALSE, warning=FALSE>>=
#source("writeup.R")
load("writeup.rda")
@
<<errortable, echo=FALSE, warning=FALSE>>=
#source("errors_table.R")
NULL
@

@@

<<reshapedata, echo=FALSE>>=
df <- read.csv("output.csv")
df2 <- df[c("penalty_fn", "ignore_cost", "assume_cost", "sigma_g", "reduction")] # subset
df3 <- reshape2::melt(df2, id = c("penalty_fn", "sigma_g", "reduction")) 
df3$reduction <- as.factor(df3$reduction)
reduction_table <- read.csv('reduction_table.csv', row.names=1)
reduction_coefs <- melt(data.frame(penalty_fn = rownames(reduction_table), reduction_table), id = "penalty_fn")[c(1,3)]
names(reduction_coefs) <- c("penalty_fn", "coefficient")
@

@@

<<Table_1, results="asis">>=
df4 <- df[c(2,4,6,9,10)]
df4 <- plyr::arrange(df4, reduction)
df5 <- subset(df4, sigma_g == 0.20)[-4]
df5 <- cbind(df5, reduction_coefs[2])
df5 <- plyr::arrange(df5, penalty_fn)
names(df5) <- c("penalty fn", "ignoring", "assuming", "percent reduction", "c2")
print(xtable::xtable(df5, caption="Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent. Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.  Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.  Column c2 shows the coefficient chosen to achieve that reduction. Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."))
@

### 2014-03-18 inst/doc/policycosts/policycosts.tex
updates
updates from previous runs

\documentclass{article}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

@@

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_7}

\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Wed Nov  6 20:50:41 2013
\begin{table}[ht]
\centering
\begin{tabular}{rlrrrrrr}
  \hline
 & penalty\_fn & ignore\_cost & ignore\_fraction & assume\_cost & assume\_fraction & sigma\_g & reduction \\ 
  \hline
1 & L1 & 14536.09 & 1.00 & 16857.61 & 1.00 & 0.05 & 0.10 \\ 
  2 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.10 \\ 
  3 & fixed & 13584.97 & 0.92 & 17582.78 & 1.05 & 0.05 & 0.10 \\ 
  4 & L1 & 9273.66 & 1.09 & 17561.81 & 1.04 & 0.05 & 0.20 \\ 
  5 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.20 \\ 
  6 & fixed & 8332.45 & 0.84 & 17401.82 & 1.03 & 0.05 & 0.20 \\ 
  7 & L1 & -641.78 & 0.21 & 15451.25 & 0.92 & 0.05 & 0.30 \\ 
  8 & L2 & -272586.11 & -24.90 & 11567.12 & 0.69 & 0.05 & 0.30 \\ 
  9 & fixed & -1213.01 & -0.46 & 15519.95 & 0.92 & 0.05 & 0.30 \\ 
  10 & L1 & 18281.97 & 1.01 & 20973.56 & 0.99 & 0.20 & 0.10 \\ 
  11 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.10 \\ 
  12 & fixed & 16691.94 & 1.03 & 20143.80 & 0.95 & 0.20 & 0.10 \\ 
  13 & L1 & 12788.95 & 0.96 & 20663.21 & 0.97 & 0.20 & 0.20 \\ 
  14 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.20 \\ 
  15 & fixed & 12399.01 & 0.88 & 21289.21 & 1.00 & 0.20 & 0.20 \\ 
  16 & L1 & 9099.48 & 0.73 & 19999.07 & 0.94 & 0.20 & 0.30 \\ 
  17 & L2 & -6337.76 & -0.39 & 17765.33 & 0.83 & 0.20 & 0.30 \\ 
  18 & fixed & 7399.01 & 0.62 & 21969.84 & 1.03 & 0.20 & 0.30 \\ 
  19 & L1 & 30227.43 & 1.07 & 31377.07 & 0.94 & 0.50 & 0.10 \\ 
  20 & L2 & 33472.18 & 1.00 & 33472.18 & 1.00 & 0.50 & 0.10 \\ 
  21 & fixed & 28926.73 & 1.09 & 30500.85 & 0.91 & 0.50 & 0.10 \\ 
  22 & L1 & 24157.93 & 1.10 & 31767.92 & 0.95 & 0.50 & 0.20 \\ 
  23 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.20 \\ 
  24 & fixed & 23573.19 & 1.02 & 30069.80 & 0.90 & 0.50 & 0.20 \\ 
  25 & L1 & 21086.12 & 1.12 & 32035.93 & 0.96 & 0.50 & 0.30 \\ 
  26 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.30 \\ 
  27 & fixed & 17209.56 & 0.85 & 32946.24 & 0.98 & 0.50 & 0.30 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

@@

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: pdgControl\\\#\# Loading required package: reshape2\\\#\# Loading required package: ggplot2\\\#\# Loading required package: data.table\\\#\# Loading required package: plyr\\\#\# Loading required package: xtable}}\end{kframe}
\end{knitrout}

@@

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{rlrrrr}
  \hline
 & penalty fn & ignoring & assuming & percent reduction & c2 \\ 
  \hline
1 & L1 & 0.81 & 1.00 & 0.10 & 0.40 \\ 
  2 & L1 & 0.62 & 0.99 & 0.20 & 0.81 \\ 
  3 & L1 & 0.35 & 0.97 & 0.30 & 2.02 \\ 
  4 & L2 & 0.68 & 0.95 & 0.10 & 0.81 \\ 
  5 & L2 & 0.44 & 0.89 & 0.20 & 1.62 \\ 
  6 & L2 & -0.28 & 0.81 & 0.30 & 2.83 \\ 
  7 & fixed & 0.78 & 1.00 & 0.10 & 3.64 \\ 
  8 & fixed & 0.56 & 0.99 & 0.20 & 8.08 \\ 
  9 & fixed & 0.31 & 0.97 & 0.30 & 12.93 \\ 
   \hline
\end{tabular}
\caption{Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent. Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.  Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.  Column c2 shows the coefficient chosen to achieve that reduction. Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs.}
\end{center}
\end{table}
